Hybrid nonlinear system identification using neural networks

### 2020-11-24 systemID_NNs.tex
sysID.

\begin{align*}
  \underset{u_s}{\textnormal{min}} & \quad \ell(y_s, u_s) \\
  x_s &= f(x_s, u_s)\\ 
  y_s &= h(x_s)
\end{align*}
in which $x_s$, $y_s$, $u_s$ are the state, output, and control respectively at
steady-states. For the nonlinear reactor example, the cost is chosen as
$\ell(y_s, u_s) = c_1C_{Af} - c_2C_B$, which measures the raw material
cost and product profit. The Figure \ref{fig:cost_curves} shows the 
cost curves of the plant, grey-box, black-box, and hybrid model 
obtained with 8 hours of training data.

@@

\begin{figure}[!h]
  \centering
  \includegraphics[page=4, width=\textwidth]{tworeac_plots_nonlin.pdf}
  \caption{Steady-state cost curve for the nonlinear plant, grey-box, black-box,
  residual, and hybrid model after training with 10 hours of data.}
  \label{fig:cost_nonlinear_10hours}
\end{figure}

\section{Conclusion}
Hey.
%\begin{figure}[!h] \centering \includegraphics[page=1,
%  width=\textwidth]{tworeac_distmodels_nonlin.pdf} \caption{Steady state
%  grey-box states and disturbance estimates based on output and input
%  disturbance models} \label{fig:cost_nonlinear_10hours} \end{figure}

>>>>

\begin{align*}
  \underset{u_s}{\textnormal{min}} & \quad \ell(y_s, u_s) \\
  x_s &= f(x_s, u_s)\\ 
  y_s &= h(x_s)
\end{align*}
in which $x_s$, $y_s$, $u_s$ are the state, output, and control respectively at
steady-states. For the nonlinear reactor example, the cost is chosen as
$\ell(y_s, u_s) = c_1C_{Af} - c_2C_B$, which measures the raw material cost and
product profit. The Figure \ref{fig:cost_curves} shows the cost curves of the
plant, grey-box, black-box, and hybrid model obtained with 8 hours of training
data. We first notice from the cost curve of the grey-box model that an
optimization with the grey-box model results in the optimizer recommending a
full supply of the raw material $A$. Since some of the product $B$ reacts to
form an undesired side product $C$ in the plant, this recommendation incurres a
cost as observed from the plant cost curve. An intuitive approach to correct
this type of plant-model mismatch is to augment the grey-box model with
integrating disturbance models and estimate the plant model mismatch from data
at one steady state. This strategy however, cannot recover the plant cost curve
in the entire actuator constraint set as the integrating disturbance models are
often linear. We notice that the cost curve of the hybrid model is almost the
same as the cost curve of the plant model in the entire actuator constraint set.
The cost curve of the black-box model is also shown and we notice that it is not
as closely aligned with the plant as compared to the hybrid model.

@@

\begin{figure}[!h]
  \centering
  \includegraphics[page=7, width=\textwidth]{tworeac_plots_nonlin.pdf}
  \caption{Steady-state cost curve for the nonlinear plant, grey-box, black-box,
  residual, and hybrid model after training with 10 hours of data.}
  \label{fig:cost_error_bb}
\end{figure}

Finally, we analyze the variation in the cost curves of the black-box and hybrid
models with increasing number of training samples. We analyze the following cost
error metric in the entire actuator constraint set
\begin{align*}
  e(u_s) = \vert \ell(y_p(u_s), u_s) - \ell(y_m(u_s), u_s) \vert
\end{align*}
in which $y_p(\cdot)$ and $y_m(\cdot)$ denote the plant and model steady state
output respectively. The Figures \ref{fig:cost_error_bb} and
\ref{fig:cost_error_hybrid} show the variation in this cost error metric in the
actuator constraint set with increasing number of training samples for the
black-box and hybrid model respectively. We observe that with an increase in the
number of training samples, the error metric for the hybrid model approaches
near zero values for a wide range of actuator values in the constraint set. The
error metric of the black-box model remains relatively larger than that of the
hybrid model in the constraint set with increase in training data. The
implication of this error metric going to zero for all actuator values in the
constraint set is that the optimum computed for the steady-state economic
optimization problem with the trained model will be the same as the true plant
optimum.

\begin{figure}[!h]
  \centering
  \includegraphics[page=8, width=\textwidth]{tworeac_plots_nonlin.pdf}
  \caption{Steady-state cost curve for the nonlinear plant, grey-box, black-box,
  residual, and hybrid model after training with 10 hours of data.}
  \label{fig:cost_error_hybrid}
\end{figure}
